---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# ezcox: Easily Process a Batch of Cox Models

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/ezcox)](https://CRAN.R-project.org/package=ezcox)
[![](http://cranlogs.r-pkg.org/badges/grand-total/ezcox?color=blue)](https://cran.r-project.org/package=ezcox)
[![HitCount](http://hits.dwyl.io/ShixiangWang/ezcox.svg)](http://hits.dwyl.io/ShixiangWang/ezcox)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/ShixiangWang/ezcox?branch=master&svg=true)](https://ci.appveyor.com/project/ShixiangWang/ezcox)
[![Travis build status](https://travis-ci.org/ShixiangWang/ezcox.svg?branch=master)](https://travis-ci.org/ShixiangWang/ezcox)
[![Codecov test coverage](https://codecov.io/gh/ShixiangWang/ezcox/branch/master/graph/badge.svg)](https://codecov.io/gh/ShixiangWang/ezcox?branch=master)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
<!-- badges: end -->

The goal of ezcox is to operate a batch of univariate or multivariate Cox models and return tidy result.

## Installation

You can install the released version of ezcox from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("ezcox")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("ShixiangWang/ezcox")
```

Visualization feature of **ezcox** needs the recent version of **forestmodel**, please run the following commands:

```r
remotes::install_github("ShixiangWang/forestmodel")
```

## Example

This is a basic example which shows you how to get result from a batch of cox models.

```{r example}
library(ezcox)
data("lung", package = "survival")

# Build unvariable models
ezcox(lung, covariates = c("age", "sex", "ph.ecog"))

# Build multi-variable models
# Control variable 'age'
ezcox(lung, covariates = c("sex", "ph.ecog"), controls = "age")
```

## Citation

* Wang, Shixiang, et al. “The predictive power of tumor mutational burden in lung cancer immunotherapy response is influenced by patients’ sex.” International journal of cancer (2019).
