---
title: "ezcox: Easily Process a Batch of Cox Models"
author: "Shixiang Wang <w_shixiang@163.com>"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ezcox}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The goal of ezcox is to operate a batch of univariate or multivariate Cox models and return tidy result.

## Installation

You can install the released version of ezcox from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("ezcox")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ShixiangWang/ezcox")
```
## Example

This is a basic example which shows you how to get result from a batch of cox models.

```{r example}
library(ezcox)
data("lung", package = "survival")

# Build unvariable models
ezcox(lung, covariates = c("age", "sex", "ph.ecog"))

# Build multi-variable models
# Control variable 'age'
ezcox(lung, covariates = c("sex", "ph.ecog"), controls = "age")
```

## Filter

Sometimes, we may need to filter result from multi-variable models.

```{r}
zz = ezcox(lung, covariates = c("sex", "age"), controls = "ph.ecog")
zz

filter_ezcox(zz, c("0", "2"))
filter_ezcox(zz, c("0", "2"), type = "contrast")
filter_ezcox(zz, c("0", "2"), type = "ref")
# More see ?filter_ezcox
```

## Get models

Get raw models may help users understand the detail and do further visualization.

```{r}
zz = ezcox(lung, covariates = c("sex", "ph.ecog"), controls = "age", return_models=TRUE)
mds = get_models(zz)
str(mds)
```

## Show models

TODO

## Citation

* Wang, Shixiang, et al. “The predictive power of tumor mutational burden in lung cancer immunotherapy response is influenced by patients’ sex.” International journal of cancer (2019).
